Supplementary information for The transboundary nature of the world’s exploited marine species

### 2020-12-09 Scripts/Manuscript_Draft.Rmd
Adressing TC comments

Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], were each responsible for over 5.8 million tonnes of transboundary species catch annually, on average, between 2005 and 2014 (Figure \@ref(fig:ffvFigureS1)). Peru's catches consisted mainly of Peruvian anchoveta (*Engraulis ringens*) and accounted for 79% of the national transboundary species production. Peru and Chile recently signed an agreement to work towards standardized stock assessments through coordinated management of the southern anchoveta stock [@UNDP:2016wp]. A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk]. Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; Df(16,158) = 2.265, p = 0.005, $\alpha$ = 0.05). China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes). Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:ffvFigure2)). As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:ffvTableS1). However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014. At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, Df(16,165) = 3.267, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.05; Figure \@ref(fig:ffvFigure2)).

```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by Km2 and UN sub-region. a) Revenue in thousand 2019 USD. b) Catch in tonnes. Points = sub-region mean \u00B1 s.d. by country."}

@@

I determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figures \@ref(fig:ffvFigure3); \@ref(fig:ffvFigureS2)). While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status. Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods). I found significant differences for all catch trend categories for transboundary species (one-way ANOVA, Df(2,459) = 47.94, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, Df(2,106) = 1.885, p = 0.157; $\alpha$ = 0.05). I also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, Df(2,459) = 19.001, p < 0.001). Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:ffvTableS2)).

>>>>

Peru and Russia, having the two largest fisheries by total catch in the world [@FAO:2018KK], were each responsible for over 5.8 million tonnes of transboundary species catch annually, on average, between 2005 and 2014 (Figure \@ref(fig:ffvFigureS1)). Peru's catches consisted mainly of Peruvian anchoveta (*Engraulis ringens*) and accounted for 79% of the national transboundary species production. Peru and Chile recently signed an agreement to work towards standardized stock assessments through coordinated management of the southern anchoveta stock [@UNDP:2016wp]. A similar management agreement was signed by Russia, Japan and the USA over shared Alaskan pollock (*Theragra chalcogramma*) in the Bering Sea in 1988 [@NOAA:gX6CtUTk]. Transboundary species also make large contributions to fisheries in Eastern Asia (one-way ANOVA; DF(16,158) = 2.265, p = 0.005, $\alpha$ = 0.05). China, the world's top fish producer [@FAO:2018KK], obtains one third (5.1 million tonnes) of its total catches from transboundary species, followed by Japan (1.8 million tonnes) and South Korea (1.06 million tonnes). Differences in the regional importance of transboundary fisheries can also be illustrated in terms of catch-revenue over the area ($km^2$) of the EEZ (Figure \@ref(fig:ffvFigure2)). As an example, the aggregated EEZ area for all Northern European countries where transboundary species are present is 3.3 million $km^2$, the $6^{th}$ smallest of the 17 groups analyzed (Table \@ref(tab:ffvTableS1). However, it had the second highest average revenue (USD 26.1 thousand per $km^2$) and the highest average catch (19.9 tonnes per $km^2$) of transboundary species per EEZ area between 2005 and 2014. At the country level, countries from Western Europe accrued significantly more revenue from transboundary fisheries per $km^2$ than any other country (one-way ANOVA, DF(16,165) = 3.267, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.05; Figure \@ref(fig:ffvFigure2)).

```{r ffvFigure2, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap="Weighted benefits of transboundary species by km2 and UN sub-region. a) Revenue in thousand 2019 USD. b) Catch in tonnes. Points = sub-region mean \u00B1 s.d. by country."}

@@

I determined the catch trend of each species within each EEZ, classifying them as increasing (Category A), constant (Category B) or decreasing (Category C) (Figures \@ref(fig:ffvFigure3); \@ref(fig:ffvFigureS2)). While previous studies have demonstrated that catch trends can be used to infer whether a stock is healthy, re-building, over-exploited or collapsed [@Kleisner:2011wn], several factors can influence stock status. Our intention here is to examine where the catch trends of transboundary species differ from non-transboundary species between 2005 and 2014 relative to historic catch since 1951 (see Methods). I found significant differences for all catch trend categories for transboundary species (one-way ANOVA, DF(2,459) = 47.94, p < 0.001, $\alpha$ = 0.05; Tukey's post hoc test p $\leq$ 0.001), and no significant differences in catch trend categories for discrete species (one-way ANOVA, DF(2,106) = 1.885, p = 0.157; $\alpha$ = 0.05). I also found significant differences in catch trends when directly comparing transboundary to discrete species categories (MANOVA, DF(2,459) = 19.001, p < 0.001). Overall, transboundary species only targeted by one country are generally less likely to have a decreasing catch trend compared to instances where the shared species is fished by neighboring countries (Table \@ref(tab:ffvTableS2)).

### 2020-12-09 Scripts/supplements.Rmd
Adressing TC comments

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
library(MyFunctions)
#### Library ####
packages <- c(
  "dplyr", # Data manipulation
  "knitr",
  "kableExtra",
  "png",
  "grid",
  "janitor"
)
my_lib(packages)
```

@@

```{r ffvTableS1, eval = T, echo = F, fig.pos= "H"}
read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
  clean_names() %>% 
  filter(sub_region != "Other") %>% 
  arrange(size_entity_sum) %>% 
  rename("UN sub region" = sub_region,
         "Area of EEZs (Km^2)" = size_entity_sum) %>% 
  kable("latex",
        booktabs = T,
        caption= "Size of all the EEZs in each sub region determined by the United Nations"
        ) %>%
  kable_styling(full_width = T)
```

```{r ffvTableS2, eval = T, echo = F, fig.pos= "H", message = F, warning = F}
# read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
#   clean_names() %>% 
#   rename(
#     Category = category,
#     "Mean (s.d.) Transboundary" = mean_shared,
#     "Mean (s.d.) Discrete" = mean_discrete) %>% 
#   kable("latex",
#         booktabs = T,
#         caption= "Average (standard deviation) number of transboundary and discrete species per EEZ for each catch trend category")
read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
  clean_names() %>% 
  mutate(
    "Mean shared" = paste(round(mean_value_x,2)," \u00B1 (",round(sd_value_x,2),")",sep=""),
    "Mean not-shared" = paste(round(mean_value_y,2)," \u00B1 (",round(sd_value_y,2),")",sep="")
  ) %>%
  select(1,8:9) %>%
  filter(observation != "No Category") %>%
  rename(Category = observation) %>%
  arrange(Category) %>% 
  kable("latex",
        booktabs = T,
        caption= "Average \u00B1 (standard deviation) number of shared and non-shared transboundary species per EEZ for each catch trend category")
```

>>>>

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}
library(MyFunctions)
#### Library ####
packages <- c(
  "dplyr", # Data manipulation
  "knitr",
  # "kableExtra",
  "png",
  "grid",
  "janitor"
)
my_lib(packages)
```

@@

```{r ffvTableS1, eval = T, echo = F, fig.pos= "H"}
read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
  clean_names() %>% 
  filter(sub_region != "Other") %>% 
  arrange(size_entity_sum) %>% 
  rename("UN sub region" = sub_region,
         "Area of EEZs (Km^2)" = size_entity_sum) %>% 
  kable(
        booktabs = T,
        caption= "Size of all the EEZs in each sub region determined by the United Nations"
        )# %>%
  # kable_styling(full_width = T)
```

```{r ffvTableS2, eval = T, echo = F, fig.pos= "H", message = F, warning = F}
# read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
#   clean_names() %>% 
#   rename(
#     Category = category,
#     "Mean (s.d.) Transboundary" = mean_shared,
#     "Mean (s.d.) Discrete" = mean_discrete) %>% 
#   kable("latex",
#         booktabs = T,
#         caption= "Average (standard deviation) number of transboundary and discrete species per EEZ for each catch trend category")
read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
  clean_names() %>% 
  mutate(
    "Mean shared" = paste(round(mean_value_x,2)," \u00B1 (",round(sd_value_x,2),")",sep=""),
    "Mean not-shared" = paste(round(mean_value_y,2)," \u00B1 (",round(sd_value_y,2),")",sep="")
  ) %>%
  select(1,8:9) %>%
  filter(observation != "No Category") %>%
  rename(Category = observation) %>%
  arrange(Category) %>% 
  kable(
        booktabs = T,
        caption= "Average \u00B1 (standard deviation) number of shared and non-shared transboundary species per EEZ for each catch trend category")
```
